Haskell in Computational Biology

### 2013-05-29 jfp.tex
tuning page breaks
corrected and improved citations

@@

We~built MRFy quickly, and we expected that
higher-order functions would make MRFy easy to extend.
Each new addition to MRFy's stochastic search took at most a day
to implement.
However, the next extension we wished to make
was based on
Richard Senington's model of \emph{local
search} \cite{senington:combinators-local}, 
which does not fit our abstraction of stochastic search.
We~wound up writing a new program that adapts parts
of MRFy to work with Senington's  \texttt{local-search} package.
We're~disappointed that such similar algorithms have entirely
different interfaces,
but the adaptation took only three weeks, and the
technical results were terrific. 
Local search outperforms random hill-climbing, simulated
annealing, and the genetic algorithm.
We~therefore count the story as a success.

>>>>

% \ifpagetuning\enlargethispage{\baselineskip}\fi

@@

We~built MRFy quickly, and we expected that
higher-order functions would make MRFy easy to extend.
Each new addition to MRFy's stochastic search took at most a day
to implement.
However, the next extension we wished to make
was based on
Richard Senington's model of \emph{local
search} \cite{senington:hybrid}, 
which does not fit our abstraction of stochastic search.
We~wound up writing a new program that adapts parts
of MRFy to work with Senington's  \texttt{local-search} package.
We're~disappointed that such similar algorithms have entirely
different interfaces,
but the adaptation took only three weeks, and the
technical results were terrific. 
Local search outperforms random hill-climbing, simulated
annealing, and the genetic algorithm.
We~therefore count the story as a success.
